### 2024-03-31 output/paper/paper.qmd
Uploading quarto file

---
title: "Analyzing the Relationship between Female Fertility Rate and Female Literacy Rate in South Asia"
author: "Jagpreet Singh"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: TBD
---

```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```

# Introduction

# Data {#sec-data}

## Data Source {#sec-variables-of-interest}

## Variables of Interest

# Model {#sec-model}

## Model Justification

# Results {#sec-results}

# Discussion {#sec-discussion}

### 2024-03-31 output/paper/paper.qmd
update paper.qmd

@@
 ---
-title: "Analyzing the Relationship between Female Fertility Rate and Female Literacy Rate in South Asia"
+title: "Books and Babies: An Analysis of the Relationship between Literacy Rate and Fertility Rate in South Asia (2000-2020)"
 author: "Jagpreet Singh"

### 2024-04-01 output/paper/paper.qmd
update paper.qmd

--- 2024-03-31 output/paper/paper.qmd
@@
 fig-pos: "H"
-abstract: TBD
+abstract: This paper utilizes data from the World Bank’s Gender Statistics database to examine the relationship between the adult female literacy rate (% of females ages 15 and above) and fertility rate (total births per woman) in South Asia between 2000-2020.
+The analysis revealed a negative correlation between the two variables, indicating that as the literacy rate increased, the fertility rate decreased.
+These findings matter as they highlight the importance of investing in female education and empowerment to manage population growth and promote sustainable development.
+The insights can guide policymakers make decisions on education initiatives and reproductive health programs to further enhance socioeconomic progress in the region.
 ---

### 2024-04-02 output/paper/paper.qmd
update paper.qmd

@@
 author: "Jagpreet Singh"
+thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia"
 date: "`r format(Sys.Date(), '%B %d, %Y')`"
@@
 ---
-
 ```{r}
@@
 ```
+# Introduction
+According to the World Bank, the South Asian region comprises Afghanistan, Bangladesh, Bhutan, India, Maldives, Nepal, Pakistan, and Sri Lanka.
+It is the most populated region in the world with countries like India, Pakistan and Bangladesh which ranks among the top 10 in in terms of population size.
+Majority of these countries are also considered developing nations and play a major role in the world economy.
+In today’s globalized world where population dynamics significantly influence a country's course it is necessary to analyze gender statistics indicators such as fertility rate and female literacy rate and how they relate to each other.
+By doing so we can gain valuable insights which can help make policy decisions on female education and empowerment that inturn help manage population growth and promote sustainable development.
 
-# Introduction
+In this paper, we will examine the relationship between the fertility rate (total births per woman) and adult female literacy rate (% of females ages 15 and above) in South Asia through a linear regression analysis.
+The estimand here is how fertility rate and female literacy rate are related.
+Specifically, we will focus on South Asia, the most populated region in the world.
+We will draw data from the World Bank website.
+Based on the analysis, we found that there is a negative relationship between fertility rate and literacy rate of adult females.
+
+In section 1, we discuss the source of data used in this paper, methodologies that follow it, and data terminology.
+In section 2, we present the results of our analysis, focusing on the trajectory of fertility rate and female literacy rate over the last two decades in the region of South Asia.
+In section 3, we will analyze the trend by establishing a linear regression model.
+In section 4 we will present the result of the model in a graph.
+Finally, in section 5 we will further discuss the findings of the result.
 

### 2024-04-02 output/paper/paper.qmd
update paper.qmd

@@
 author: "Jagpreet Singh"
-thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia"
+thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia.git"
 date: "`r format(Sys.Date(), '%B %d, %Y')`"

### 2024-04-02 output/paper/paper.qmd
update paper.qmd

--- 2024-04-02 output/paper/paper.qmd
@@
 ---
-title: "Books and Babies: An Analysis of the Relationship between Literacy Rate and Fertility Rate in South Asia (2000-2020)"
+title: "Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
 author: "Jagpreet Singh"
-thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia"
+thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia.git"
 date: "`r format(Sys.Date(), '%B %d, %Y')`"

### 2024-04-18 script/02-data_cleaning.R
update, run and save output for 02-data_Cleaning.R

@@ -1,39 +1,38 @@
 #### Preamble ####
-# Purpose : Clean and merging the raw data from unedited_data_fertility_rate.csv and input/data/unedited_data_literacy_rate.csv
+# Purpose : Clean and merging the raw data to gather relevant data for analysis 
 # Author : Jagpreet Singh
-# Date : 31 March, 2024
+# Date : 17 April, 2024
 # Contact : jagpreetsingh.singh@mail.utoronto.ca
 # License : MIT
-# Prerequisite : install.packages("tidyverse") should be run if not pre-existing
+# Prerequisite : Download the global Literacy rate (adult female) and Fertility rate (total) from World Bank Open Data.
 
-#### Workspace Setup ####
 
+#### Workspace setup ####
 library(tidyverse)
-options(warn = -1)
+library(arrow)
 
-# Define file paths
-fertility_file <- "input/data/unedited_data_fertility_rate.csv"
-literacy_file <- "input/data/unedited_data_literacy_rate.csv"
-output_file <- "output/data/edited_data.csv"
+#### Clean data ####
 
-# Suppressing message while reading CSV files
-suppressMessages({
-  # Read the CSV files, selecting the Time and respective columns
-  fertility_data <- read_csv(fertility_file) %>%
-    filter(Time <= 2020) %>%
-    select(Time, `South Asia [SAS] - Fertility rate, total (births per woman) [SP.DYN.TFRT.IN]`) %>%
-    rename(Year = Time, Fertility_rate = `South Asia [SAS] - Fertility rate, total (births per woman) [SP.DYN.TFRT.IN]`)
-  
-  literacy_data <- read_csv(literacy_file) %>%
-    filter(Time <= 2020) %>%
-    select(Time, `South Asia [SAS] - Literacy rate, adult female (% of females ages 15 and above) [SE.ADT.LITR.FE.ZS]`) %>%
-    rename(Year = Time, Literacy_Rate = `South Asia [SAS] - Literacy rate, adult female (% of females ages 15 and above) [SE.ADT.LITR.FE.ZS]`)
-})
+# Read the fertility rate, total data
+fertility_rate_data <- read_csv("data/raw_data/API_SP.DYN.TFRT.IN_DS2_en_csv_v2_43477.csv", skip = 4)
+south_asia_fertility_rate <- fertility_rate_data %>% 
+  filter(`Country Name` == "South Asia") %>% 
+  select(`2000`:`2020`) %>% 
[…]

### 2024-04-18 script/02-data_cleaning.R
update 02-data_cleaning.R and uploading output

@@ -25,7 +25,7 @@ female_literacy_rate_data <- read_csv("data/raw_data/API_SE.ADT.LITR.FE.ZS_DS2_e
 south_asia_literacy_rate <- female_literacy_rate_data %>% 
   filter(`Country Name` == "South Asia") %>% 
   select(`2000`:`2020`) %>% 
-  pivot_longer(cols = everything(), names_to = "Year", values_to = "female_literacy_Rate")
+  pivot_longer(cols = everything(), names_to = "Year", values_to = "female_literacy_rate")
 
 # Combine the datasets
 combined_data <- left_join(south_asia_fertility_rate, south_asia_literacy_rate, by = "Year")

### 2024-04-18 script/01-download_data.R
updated 01-download_Data.R

@@ -1,20 +1,13 @@
 #### Preamble ####
-# Purpose: Gather the relevant points, clean up the column names and refine their values
+# Purpose: Instructions to download raw data from the World Bank Open Data
 # Author: Jagpreet Singh
-# Data: 31 March, 2024
+# Data: 17 April, 2024
 # Contact: jagpreetsingh.singh@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Access to the World Bank Literacy rate, adult female (% of femaleas ages 15 and above) and Fertility rate, total (births per woman) data.
-
-#### Workspace setup ####
-library(tidyverse)
+# Pre-requisites: None
 
 #### Download data ####
 
-##Data was downloaded from https://data.worldbank.org/indicator/SE.ADT.LITR.FE.ZS?locations=8S&name_desc=true&view=map and https://genderdata.worldbank.org/indicators/sp-dyn-tfrt-in/ from the individual data sets.
-##Data sets for years 2000 - 2020 were downloaded manually.
-
-#### Save data ####
-
-fertility_rate <- read_csv(here::here("input/data/unedited_data_fertility_rate.csv"))
-literacy_rate <- read_csv(here::here("input/data/unedited_data_literacy_rate.csv"))
+# Fertility rate, total (births per woman) dataset was downloaded from: https://data.worldbank.org/indicator/SP.DYN.TFRT.IN
+# Literacy rate, adult female dataset was downloaded from: https://data.worldbank.org/indicator/SE.ADT.LITR.FE.ZS?locations=8S&name_desc=true&view=map
+# Once open the website, find 'download' and click 'csv'

### 2024-04-18 script/02-data_cleaning.R
updated 02-data_cleaning.R

@@ -4,8 +4,7 @@
 # Date : 17 April, 2024
 # Contact : jagpreetsingh.singh@mail.utoronto.ca
 # License : MIT
-# Prerequisite : Download the global Literacy rate (adult female) and Fertility rate (total) from World Bank Open Data.
-
+# Prerequisite : Download the global Literacy rate (adult female) and Fertility rate (total) from World Bank Open Data. Instal packages : Arrow and Tidyverse
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-04-18 script/02-data_cleaning.R
update script for data cleaning

@@ -30,8 +30,8 @@ south_asia_literacy_rate <- female_literacy_rate_data %>%
 combined_data <- left_join(south_asia_fertility_rate, south_asia_literacy_rate, by = "Year")
 
 # Save the combined data to a new CSV file
-write_csv(combined_data, "data/analysis_data/south_asia_2000_2020.csv")
+write_csv(combined_data, "data/analysis_data/cleaned_data_south_asia_2000_2020.csv")
 
-write_parquet(combined_data, "data/analysis_data/south_asia_2000_2020.parquet")
+write_parquet(combined_data, "data/analysis_data/cleaned_data_south_asia_2000_2020.parquet")
 
 

### 2024-04-18 script/00-simulate_data.R
update 00-simulate_data.r and upload outpput

@@ -16,9 +16,9 @@ set.seed(123)
 # Generate simulated data
 simulated_data <- tibble(
   Year = seq(2000, 2020, by = 1),
-  Fertility_Rate = round(seq(3.572, 2.267, length.out = 21) + rnorm(21, mean = 0, sd = 0.1), 3),
-  Literacy_Rate = round(seq(44.928, 64.607, length.out = 21) + rnorm(21, mean = 0, sd = 0.1), 3)
+  fertility_rate_total = round(seq(3.572, 2.267, length.out = 21) + rnorm(21, mean = 0, sd = 0.1), 3),
+  female_literacy_rate = round(seq(44.928, 64.607, length.out = 21) + rnorm(21, mean = 0, sd = 0.1), 3)
 )
 
 # Save the simulated data to a CSV file
-write.csv(simulated_data, file = "output/data/simulated_data.csv", row.names = FALSE)
+write.csv(simulated_data, file = "data/analysis_data/simulated_data.csv", row.names = FALSE)

### 2024-04-18 script/00-simulate_data.R
update simulata_data

@@ -16,8 +16,8 @@ set.seed(123)
 # Generate simulated data
 simulated_data <- tibble(
   Year = seq(2000, 2020, by = 1),
-  fertility_rate_total = round(seq(3.572, 2.267, length.out = 21) + rnorm(21, mean = 0, sd = 0.1), 3),
-  female_literacy_rate = round(seq(44.928, 64.607, length.out = 21) + rnorm(21, mean = 0, sd = 0.1), 3)
+  fertility_rate_total = round(seq(3.572, 2.267, length.out = 21) + rnorm(21, mean = 0, sd = 0.1)),
+  female_literacy_rate = round(seq(44.928, 64.607, length.out = 21) + rnorm(21, mean = 0, sd = 0.1))
 )
 
 # Save the simulated data to a CSV file

### 2024-04-18 script/00-simulate_data.R
update 00-simulate_data

@@ -16,8 +16,8 @@ set.seed(123)
 # Generate simulated data
 simulated_data <- tibble(
   Year = seq(2000, 2020, by = 1),
-  fertility_rate_total = round(seq(3.572, 2.267, length.out = 21) + rnorm(21, mean = 0, sd = 0.1)),
-  female_literacy_rate = round(seq(44.928, 64.607, length.out = 21) + rnorm(21, mean = 0, sd = 0.1))
+  fertility_rate_total = round(seq(3.572, 2.267, length.out = 21) + rnorm(21, mean = 0, sd = 0.1),5),
+  female_literacy_rate = round(seq(44.928, 64.607, length.out = 21) + rnorm(21, mean = 0, sd = 0.1),5)
 )
 
 # Save the simulated data to a CSV file

### 2024-04-18 script/03-test_data.R
uploading script to test data

@@ -1,0 +1,50 @@
+#### Preamble ####
+# Purpose: Tests a dataset to ensure it's validity.
+# Author: Jagpreet Singh
+# Data: 17 April 2024
+# Contact: jagpreetsingh.singh@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 02-data_cleaning.R
+
+#### Workspace setup ####
+library(tidyverse)
+library(dplyr)
+
+#### Read data ####
+cleaned_data_south_asia_2000_2020 <- read.csv("data/analysis_data/cleaned_data_south_asia_2000_2020.csv")
+
+#### Test data ####
+
+# Test if there are 21 years
+cleaned_data_south_asia_2000_2020$Year |> min(na.rm = TRUE) >=21
+
+
+# Test for zero or blank values in the fertility_rate_total column
+zero_blank_test <- cleaned_data_south_asia_2000_2020 %>%
+  filter(!is.na(fertility_rate_total) & fertility_rate_total != 0) %>%
+  nrow() == nrow(cleaned_data_south_asia_2000_2020)
+
+# Output the result
+print(zero_blank_test)
+
+# Test for zero or blank values in the female_literacy_rate column
+zero_blank_test <- cleaned_data_south_asia_2000_2020 %>%
+  filter(!is.na(female_literacy_rate) & female_literacy_rate != 0) %>%
+  nrow() == nrow(cleaned_data_south_asia_2000_2020)
+
+# Output the result
+print(zero_blank_test)
+
+# Test for matching values between fertility_rate_total and female_literacy_rate columns for each year
+matching_values <- cleaned_data_south_asia_2000_2020 %>%
+  group_by(Year) %>%
+  filter(!is.na(fertility_rate_total) & !is.na(female_literacy_rate)) %>%
+  filter(fertility_rate_total == female_literacy_rate) %>%
+  ungroup()
+
+# Output the result
+if (nrow(matching_values) > 0) {
+  print("Test Failed: Some values in fertility_rate_total match female_literacy_rate for one or more years.")
+} else {
+  print("Test Passed: No values in fertility_rate_total match female_literacy_rate for any given year.")
+}

### 2024-04-18 other/datasheet/datasheet_template.qmd
upload datasheet_template.pdf and datasheet_template.qmd

---
title: "Datasheet for 'Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)'"
author: "Jagpreet Singh"
thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia.git"
date: today
date-format: long
format: pdf
number-sections: true
bibliography: datasheet_ref.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to analyze the relationship between literacy rate, adult female (% of females ages 15 and above) and fertility rate, total (births per woman) in South Asia.There is not gap to be filled.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Jagpreet Singh, Student at the University of Toronto
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - Not Applicable
4. *Any other comments?*
    - No

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each row represents female literacy rate and fertility rate for a given year.
2. *How many instances are there in total (of each type, if appropriate)?*
	- 21
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- Dataset contains a sample representing fertility rate and literacy rate between 2000-2020 for South Asia. The larger set comprise of data for various countries over various years.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Female literacy rate, Fertility rate
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- No
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- No
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- No
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- No
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- No
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- No
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- No
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- The data were gathered from the World Bank Data Bank
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Scraping and parsing using R.
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- Sampled data over 20 years for the region of interest
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- Jagpreet Singh, student
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- April 17, 2024
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- Third parties 
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- No
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- No
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- No
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
12. *Any other comments?*
	- No

**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
	- Yes cleaning of the data was done.
2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
	- No
3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
	- R was used.
4. *Any other comments?*
	- No

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- No
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No
3. *What (other) tasks could the dataset be used for?*
	- data can be used to study trends for each variable on its own
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No
6. *Any other comments?*
	- No

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
	- The dataset is available through GitHub.
2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
	- GitHub
3. *When will the dataset be distributed?*
	- The dataset is available now.
4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
	- No. MIT License
5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
	- None 
6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
	- None 
7. *Any other comments?*
	- No

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
	- Jagpreet Singh
2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
	- jagpreetsingh.singh@mail.utoronto.ca
3. *Is there an erratum? If so, please provide a link or other access point.*
	- No
4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
	- No
5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
	- No
6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
	- No
7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
	- Pull request on GitHub.
8. *Any other comments?*
	- No

\newpage

# References

### 2024-04-18 script/04-model.R
upload script 04-model.R

@@ -1,0 +1,28 @@
+#### Preamble ####
+# Purpose: Simple Linear Regression Model for relationship between female literacy rate and fertility rate in South Asia between 2000-2020
+# Author: Jagpreet Singh
+# Data: 17 April 2024
+# Contact: jagpreetsingh.singh@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: 02-data_cleaning.R and run install.packages("modelsummary")
+
+#### Workspace setup ####
+library(tidyverse)
+library(modelsummary)
+
+#### Read data ####
+analysis_data <- read.csv("data/analysis_data/cleaned_data_south_asia_2000_2020.csv")
+
+#### Create model ####
+
+# Fit a linear model
+model <- lm(female_literacy_rate ~ fertility_rate_total, data = analysis_data)
+
+# Summary of the model to see results
+modelsummary::modelsummary(
+  list("Fertility rate" = model),
+  fmt = 2
+)
+
+#### Save model ####
+saveRDS(model, "models/linear_model.rds")

### 2024-04-18 script/04-model.R
update model.R

@@ -16,11 +16,11 @@ analysis_data <- read.csv("data/analysis_data/cleaned_data_south_asia_2000_2020.
 #### Create model ####
 
 # Fit a linear model
-model <- lm(female_literacy_rate ~ fertility_rate_total, data = analysis_data)
+model <- lm(fertility_rate_total ~ female_literacy_rate, data = analysis_data)
 
 # Summary of the model to see results
 modelsummary::modelsummary(
-  list("Fertility rate" = model),
+  list("Female Literacy Rate" = model),
   fmt = 2
 )
 

### 2024-04-18 paper/paper.qmd
update paper.qmd

--- 2024-04-02 output/paper/paper.qmd
@@
 ---
+
 ```{r}
@@
 ```
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+library(tidyverse)
+library(here)
+library(readr)
+library(dplyr)
+library(ggplot2)
+library(modelsummary)
+
+analysis_data <- read_csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
+
+```
+
 # Introduction
@@
 
+\newpage
+
 # Model {#sec-model}
+
+Based on the preliminary analysis, we observed a negative relationship between fertility rate, total (births per woman) and literacy rate, adult females (% of females ages 15 and above).
+This indicates a potential linear regression.
+
+Below is the equation of the linear regression model:
+
+$$ 
+Yij = β0 + β1Xij + εij
+$$
+where:
+
+-   $Y$ is the Fertility Rate
+
+-   $X$ is the Female Literacy Rate
+
+-   $Y_{ij}$ is the Fertility Rate for observation j in year i.
+
+-   $X_{ij}$ is the Female Literacy Rate for observation j in year i.
+
+-   $\beta_0$ is the intercept/constant term, which represents the expected value of Fertility Rate when the Female Literacy Rate is equal to zero.
+
+-   $\beta_1$ is the slope coefficient or the estimated change in Fertility Rate for a one-unit increase in the Female Literacy Rat.
+
+-   $\epsilon_{ij}$ is the error term or the deviation of the actual value of Fertility Rate from the predicted value based on the regression equation.
+
+This linear regression model aims to estimate the values of β0 and β1 such that the model fits the data well, and predicts the expected value of the Fertility Rate for different values of the Female Literacy Rate.
+The statistical significance of β1 can be assessed using a t-test, which tests whether the estimated coefficients are significantly different from zero.
+If the p-value of the t-test is less than the selected level of significance, we can conclude that there is a significant relationship between the Female Literacy Rate and the Fertility Rate.
+
+\newpage
+
+# Results {#sec-results}
+
+```{r}
+#| label: fig-3
+#| fig-cap: "The model shows the relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
+#| echo: false
+#| warning: false
+
+library(ggplot2)
+
+analysis_data %>%
+  ggplot(aes(x = `female_literacy_rate`, y = `fertility_rate_total`)) +
+  geom_point(alpha = 0.5) +
+  geom_smooth(method = "lm", se = TRUE, color = "black", linetype = "solid") +
+  labs(x = "Literacy Rate, Adult Females (% of females ages 15 and above)", y = "Fertility Rate, Total (births per woman)") +
+  theme_classic()
+
+```
 
@@
 
-# Results {#sec-results}
-
 # Discussion {#sec-discussion}

### 2024-04-18 script/00-simulate_data.R
update simulate_data.R

@@ -9,6 +9,7 @@
 
 # Load necessary libraries
 library(tidyverse)
+library(dplyr)
 
 # Set seed for reproducibility
 set.seed(123)

### 2024-04-18 script/02-data_cleaning.R
update data_cleaning script

@@ -7,7 +7,7 @@
 # Prerequisite : Download the global Literacy rate (adult female) and Fertility rate (total) from World Bank Open Data. Instal packages : Arrow and Tidyverse
 
 #### Workspace setup ####
-library(tidyverse)
+library(tidyverse) 
 library(arrow)
 
 #### Clean data ####

### 2024-04-18 paper/paper.qmd
update paper.qmd

@@
 
-analysis_data <- read_csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
+analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
 
@@
 
+```{r, results='asis'}
+#| echo: false
+#| warning: false
+#| label: tbl-data
+#| tbl-cap: "A summary table of cleaned data"
+
+library(knitr)
+
+kable(analysis_data)
+
+```
 ## Data Source {#sec-variables-of-interest}
@@
 #| warning: false
-
 library(ggplot2)
@@
   theme_classic()
-
 ```

### 2024-04-18 paper/paper.qmd
upload paper.qmd and llm usage2

@@
 knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
-```
-```{r}
-#| include: false
-#| warning: false
-#| message: false
-
-library(tidyverse)
-library(here)
-library(readr)
-library(dplyr)
-library(ggplot2)
-library(modelsummary)
-
-analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
-
 ```
@@
 
-# Data {#sec-data}
+# Data
 
+## Data Description and Methodology
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+library(tidyverse)
+library(here)
+library(readr)
+library(dplyr)
+library(ggplot2)
+library(modelsummary)
+
+analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
+
+```
 ```{r, results='asis'}
@@
 ```
-## Data Source {#sec-variables-of-interest}
+
+## Data Visualization
+
+### Trend of Female Literacy Rate in South Asia (2000-2020)
+
+```{r fig.width=12, fig.height=8}
+#| label: fig-1
+#| fig-cap: literacy rate, adult females (% of females ages 15 and above) in South Asia (2000-2020) 
+#| echo: false
+#| warning: false
+# Load necessary libraries
+library(ggplot2)
+library(here)
+
+# Read data from CSV file
+analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
+
+# Create ggplot
+ggplot(data = analysis_data, aes(x = Year, y = female_literacy_rate)) +
+  geom_line(color = "dark green") +  # Change to line graph
+  labs(x = "Year", y = "Female Literacy Rate (% of females ages 15 and above)")
+```
+
+### Trend of Fertility Rate in South Asia (2000-2020)
+
+```{r fig.width=12, fig.height=8}
+#| label: fig-2
+#| fig-cap: literacy rate, Fertility Rate, Total (births per woman) in South Asia (2000-2020) 
+#| echo: false
+#| warning: false
+# Load necessary libraries
+library(ggplot2)
+library(here)
+
+# Read data from CSV file
+analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
+
+# Create ggplot
+ggplot(data = analysis_data, aes(x = Year, y = fertility_rate_total)) +
+geom_line(color = "red") +  # Change to line graph
+  labs(x = "Year", y = "Fertility Rate, Total (births per woman)")
+```
 
@@
 
+```{r, results='asis'}
+#| label: tbl-model
+#| tbl-cap: "T-Value and P-Value of Regression"
+#| echo: false
+#| warning: false
+library(knitr)
+
+library(modelsummary)
+
+loaded_model <- readRDS(here::here("models/linear_model.rds"))
+
+model_summary <- summary(loaded_model)
+
+t_values <- model_summary$coefficients[, "t value"]
+p_values <- model_summary$coefficients[, "Pr(>|t|)"]
+
+summary_df <- data.frame(t_value = t_values, p_value = p_values)
+kable(summary_df)
+```
+
 ## Model Justification

### 2024-04-18 paper/paper.qmd
update paper.qmd

@@
 ## Data Description and Methodology
+
+The data used in this paper was obtained from the World Bank's Data Bank which is publicly available on the Data Bank website [@The_World_Bank_2024a].
+A considerable amount of the data in the World Bank's Data Bank is gathered and compiled by the World Bank itself, along with information from other reliable public and private sector sources, international organizations, national statistical offices, and specialized agencies of the United Nations (UN).
+The World Bank then compiles and examines these data to find patterns and provide guidance in policy matters.
+
+The two datasets that are used in this paper are fertility rate (total births per woman)[@The_World_Bank_2024c] and literacy rate, adult females (% of females ages 15 and above) [@The_World_Bank_2024b].
+Both female literacy rate and fertility rate data was available for a total of 266 regions including individual countries and group of countries (for example - South Asia, Middle East etc.).
+While the literacy rate data was available from year 1960 to 2022, the fertility rate data consisted of data from 1960 to 2021.
+Not every country had data available for each year.
+The region of interest for this study is South Asia and the time period selected was 2000-2020.
+Both fertility rate and female literacy rate data was available for South Asia for the specified time period.
+The two indicators were merged to form a new data set with 21 rows that gives both fertility rate and female literacy rate in South Asia for any given year between 2000-2020.Total fertility rate represents the number of children that would be born to a woman if she were to live to the end of her childbearing years and bear children in accordance with age-specific fertility rates of the specified year.
+Female Adult literacy rate is the percentage of females ages 15 and above who can both read and write with understanding a short simple statement about their everyday life.
+
 ```{r}
@@
 
+@tbl-data shows the cleaned data with 21 observations from year 2000-2020. Here, fertility_rate_total and female_literacy_rate are the 2 variables of interest.
+
+The data was cleaned and analyzed using the 'R' programming language[@citeR] and the following packages were used: 'tidyverse' [@tidyverse], 'janitor' [@janitor],`dplyr` [@Dplyr], `ggplot2` [@citeggplot2], `here` [@herePackage], `kableExtra` [@citekableExtra], `knitr` [@knitr], `modelsummary` [@model], `readr` [@readr], `tibble` [@tibblePackage] and 'arrow' [@arrow]
+
 ## Data Visualization
@@
 #| label: fig-1
-#| fig-cap: literacy rate, adult females (% of females ages 15 and above) in South Asia (2000-2020) 
+#| fig-cap: Literacy rate, adult females (% of females ages 15 and above) in South Asia (2000-2020) 
 #| echo: false
@@
 ```
+@fig-1 represents South Asia's female literacy rate over the span of 21 years i.e.
+2000-2020.
+The literacy rate is represented as the percentage of females ages 15 and above in South Asia who can both read and write with understanding a short simple statement about their everyday life.
+The graph depicts an overall upward trend in the female literacy rate over the two decades.
+The female literacy rate in year 2000 was approximately 44.9287 % which grew consistently over the period of 21 years to reach 64.6073 % as of 2020.
+There were few minor fluctuations in the opposite direction but no drastic change was observed in the upward trend.The figure suggests that more and more females of ages 15 and above in South Asia acquired literacy over the years.There could be various social, economic and political changes that may have influenced the literacy rate over this time period.
 
@@
 #| label: fig-2
-#| fig-cap: literacy rate, Fertility Rate, Total (births per woman) in South Asia (2000-2020) 
+#| fig-cap: Fertility Rate, Total (births per woman) in South Asia (2000-2020) 
 #| echo: false
@@
 ```
-
-## Variables of Interest
+@fig-2 represents South Asia's fertility rate over the span of 21 years i.e.
+2000-2020.
+The fertility rate is represented as the number of children that would be born to a woman if she were to live to the end of her childbearing years and bear children in accordance with age-specific fertility rates of the specified year.
+The graph depicts a strictly downward trend in the fertility rate over the past two decades.
+The fertility rate in year 2000 was 3.5722 children per woman which declined over the period of 21 years to 2.2670 children per woman as of 2020.The figure suggests that females in South Asia are choosing to have lesser and lesser number of children in recent times.There could be various social, cultural, economic and political changes that may have influenced this decline in fertility rate.
 
@@
 
+@fig-3 is a depiction of a linear regression model showing the relationship between fertility rate, total (births per woman) and literacy rate, adult females (% of females ages 15 and above).
+The female literacy rate is given by the x-axis and the fertility rate is given by the y-axis.
+The solid black line indicates the trend of this relationship as estimated by the linear regression model.
+The confidence interval for the regression line is given by the grey shaded area and also represents the uncertainty around the estimated relationship.
+Analyzing the regression line, we can observe that there exists a negative relationship between fertility rate, total (births per woman) and literacy rate, adult females (% of females ages 15 and above).
+As the literacy rate increases the total number of children a woman gives birth decreases.
+The negative sloping regression line indicating a negative correlation and the confidence interval giving the range of the uncertainty, we can say that a true regression lies in this area.
+
 ```{r, results='asis'}

### 2024-04-18 paper/paper.qmd
update paper.qmd and references.bib
script to convert rds to txt

@@
 
+```{r}
+library(knitr)
+
+# Load the model from the RDS file
+loaded_model <- readRDS(here::here("models/linear_model.rds"))
+
+# Capture the console output
+output <- capture.output(summary(loaded_model))
+
+# Write the captured output to a text file
+writeLines(output, "model_summary.txt")
+
+# Render the text file as a picture
+system(paste("convert -density 300 model_summary.txt model_summary.png"))
+
+# Display the saved image
+include_graphics("model_summary.png")
+
+```
+
 ## Model Justification

### 2024-04-18 script/05-rdstotxt.R

@@ -1,0 +1,5 @@
+
+
+loaded_model <- readRDS(here::here("models/linear_model.rds"))
+model_summary <- capture.output(summary(loaded_model))
+writeLines(model_summary, "model_summary.txt")

### 2024-04-18 paper/paper.qmd
update paper.wmd, upload usage3.txt

--- 2024-04-18 paper/paper.qmd
@@
 
+```{r, results='asis'}
+#| label: tbl-model2
+#| tbl-cap: "Summary of the linear regression model"
+#| echo: false
+#| warning: false
+library(knitr)
+
+# Load the data from the RDS file
+loaded_model <- readRDS(here::here("models/linear_model.rds"))
+
+# Extract coefficients and their standard errors
+coefficients <- round(coef(loaded_model), 3)
+standard_errors <- round(summary(loaded_model)$coefficients[, "Std. Error"], 3)
+
+# Create a data frame
+model_data <- data.frame(Coefficients = coefficients, Standard_Error = standard_errors)
+
+# Render the data frame as a table using kable
+kable(model_data, format = "markdown")
+
+# Extract number of observations, R-squared value, and additional model metrics
+n_obs <- length(residuals(loaded_model))
+r_squared <- summary(loaded_model)$r.squared
+r_squared_adj <- summary(loaded_model)$adj.r.squared
+aic <- AIC(loaded_model)
+bic <- BIC(loaded_model)
+log_likelihood <- logLik(loaded_model)
+rmse <- sqrt(mean(residuals(loaded_model)^2))
+
+# Create a data frame for the model metrics
+model_metrics <- data.frame(
+  Metric = c("Num.Obs.", "R2", "R2 Adj.", "AIC", "BIC", "Log.Lik.", "RMSE"),
+  Value = c(n_obs, round(r_squared, 3), round(r_squared_adj, 3), aic, bic, log_likelihood, round(rmse, 2))
+)
+
+# Render the data frame as a table using kable
+kable(model_metrics, format = "markdown")
+
+```
+
 ## Model Justification

### 2024-04-18 script/05-rdstotxt.R

@@ -1,5 +1,0 @@
-
-
-loaded_model <- readRDS(here::here("models/linear_model.rds"))
-model_summary <- capture.output(summary(loaded_model))
-writeLines(model_summary, "model_summary.txt")

### 2024-04-19 paper/paper.qmd
Update paper.qmd

@@
 format: pdf
+number-sections: true
 fig-pos: "H"
@@
 # Introduction
+
 According to the World Bank, the South Asian region comprises Afghanistan, Bangladesh, Bhutan, India, Maldives, Nepal, Pakistan, and Sri Lanka.
@@
 
-# Model {#sec-model}
+# Model
 
@@
 $$
+
 where:
@@
 
--   $\beta_1$ is the slope coefficient or the estimated change in Fertility Rate for a one-unit increase in the Female Literacy Rat.
+-   $\beta_1$ is the slope coefficient or the estimated change in Fertility Rate for a one-unit increase in the Female Literacy Rate.
 
@@
 
-# Results {#sec-results}
+# Results
 
@@
 The negative sloping regression line indicating a negative correlation and the confidence interval giving the range of the uncertainty, we can say that a true regression lies in this area.
+
+\newpage
 
@@
 ```
+@tbl-model and Table 3 provides us with a vital summary of the regression model that further helps us to understand the relationship between fertility rate, total (births per woman) and literacy rate, adult females (% of females ages 15 and above).
+Together, these summary statistics tells us the following about our regression model:
 
-## Model Justification
+* The t-value for the female literacy rate is approximately -19.811, which means that the estimate is -19.811 standard deviations away from 0.
+The negative sign of the t-value indicates a negative relationship between female literacy rate and fertility rate in South Asia.
 
-# Discussion {#sec-discussion}
+* The t-value for the intercept is 36.95598, indicating that the estimate is significantly different from zero.
+
+* The p-value for both female literacy rate and the intercept is 0 which means that the coefficient for female literacy rate and the intercept is statistically significant at common alpha levels.
+
+* The coefficient for the intercept is approximately 6.097, suggesting that when the female literacy rate is 0, the fertility rate is predicted to be around 6.097 births per woman.
+However, interpreting the intercept as meaningful may not be appropriate as a female literacy rate of 0 is not feasible and is outside the range of the data.
+
+* The coefficient for female literacy rate is approximately -0.059, with a standard error of 0.003.This suggests that for each one-unit increase in the female literacy rate, the fertility rate is expected to decrease by 0.059 births per woman.
+The negative coefficient indicates a negative relationship between female literacy rate and fertility rate which means as female literacy rate increases, the fertility rate will decrease.
+
+* The R-squared value of 0.954 represents that approximately 95.4% of the variability in the fertility rate is explained by the model.This high R-squared value suggests a strong fit of the model to the data.
+
+In summary, this linear model suggests a statistically significant negative relationship between female literacy rate and fertility rate which means as female literacy rate increases, the fertility rate will decrease.
+However, the intercept is not statistically significant.
+While the model has a high R-squared value, indicating a strong fit to the data, the practical significance of the intercept may be questionable.
+
+# Discussion 
+\newpage
+# References

### 2024-04-19 paper/paper.qmd
update paper.qmd and upload sketches

@@
 The fertility rate in year 2000 was 3.5722 children per woman which declined over the period of 21 years to 2.2670 children per woman as of 2020.The figure suggests that females in South Asia are choosing to have lesser and lesser number of children in recent times.There could be various social, cultural, economic and political changes that may have influenced this decline in fertility rate.
-
 \newpage
@@
 $$
-
 where:
@@
 If the p-value of the t-test is less than the selected level of significance, we can conclude that there is a significant relationship between the Female Literacy Rate and the Fertility Rate.
-
-\newpage
 
@@
 The negative sloping regression line indicating a negative correlation and the confidence interval giving the range of the uncertainty, we can say that a true regression lies in this area.
-
-\newpage
 
@@
 
-In summary, this linear model suggests a statistically significant negative relationship between female literacy rate and fertility rate which means as female literacy rate increases, the fertility rate will decrease.
+The linear regression model suggests a statistically significant negative relationship between female literacy rate and fertility rate which means as female literacy rate increases, the fertility rate will decrease.
 However, the intercept is not statistically significant.
@@
 # Discussion
+
+## Growth in Female Literacy Rate in South Asia
+
+As analyzed in @fig-1,  the female literacy rate in South Asia is on the rise over the last two decades with a literacy rate of approximately 44.9 percent in the year 2000 to approximately 64.6 percent in 2020.
+This upward trend is not confined to the past two decades only.
+South Asia has made a tremendous progress in female literacy rate which was only 21.27 percent in 1975[@The_World_Bank_2024b].
+
+## Declining Fertility Rate (total births per woman)in South Asia
+
+As analyzed in @fig-2,  the fertility rate in South Asia is on the decline over the last two decades with a fertility rate of approximately 3.57 births per woman in the year 2000 to approximately 2.26 births per woman in 2020.
+This downward trend is not confined to the past two decades only.
+Fertility rate in South Asia has long been on a decline.
+The South Asian fertility rate was as high as 6.07 births per woman in 1960[@The_World_Bank_2024c].
+
+## Impact of Female Literacy Rate on Fertility Rate
+
 \newpage

### 2024-04-19 script/02-data_cleaning.R
update 02-data_cleaning.R

@@ -1,10 +1,10 @@
 #### Preamble ####
-# Purpose : Clean and merging the raw data to gather relevant data for analysis 
+# Purpose : Cleaning and merging the raw data to gather relevant data for analysis 
 # Author : Jagpreet Singh
 # Date : 17 April, 2024
 # Contact : jagpreetsingh.singh@mail.utoronto.ca
 # License : MIT
-# Prerequisite : Download the global Literacy rate (adult female) and Fertility rate (total) from World Bank Open Data. Instal packages : Arrow and Tidyverse
+# Prerequisite : Download the global Literacy rate (adult female) and Fertility rate (total) from World Bank Open Data. Install packages : Arrow and Tidyverse
 
 #### Workspace setup ####
 library(tidyverse) 

### 2024-04-19 paper/paper.qmd
update references.bib and paper.qmd

@@
 In today’s globalized world where population dynamics significantly influence a country's course it is necessary to analyze gender statistics indicators such as fertility rate and female literacy rate and how they relate to each other.
-By doing so we can gain valuable insights which can help make policy decisions on female education and empowerment that inturn help manage population growth and promote sustainable development.
+By doing so we can gain valuable insights which can help make policy decisions on female education and empowerment that in-turn help manage population growth and promote sustainable development.
 
@@
 
-The data used in this paper was obtained from the World Bank's Data Bank which is publicly available on the Data Bank website [@The_World_Bank_2024a].
+The data used in this paper was obtained from the World Bank's Data Bank which is publicly available on the Data Bank website [@The_World_Bank].
 A considerable amount of the data in the World Bank's Data Bank is gathered and compiled by the World Bank itself, along with information from other reliable public and private sector sources, international organizations, national statistical offices, and specialized agencies of the United Nations (UN).
@@
 
-The two datasets that are used in this paper are fertility rate (total births per woman)[@The_World_Bank_2024c] and literacy rate, adult females (% of females ages 15 and above) [@The_World_Bank_2024b].
+The two data sets that are used in this paper are fertility rate (total births per woman)[@The_World_Bank_Fertility] and literacy rate, adult females (% of females ages 15 and above) [@The_World_Bank_Literacy].
 Both female literacy rate and fertility rate data was available for a total of 266 regions including individual countries and group of countries (for example - South Asia, Middle East etc.).
@@
 
+# Load necessary libraries
 library(tidyverse)
@@
 
+# Read data from CSV file
 analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))
@@
 kable(analysis_data)
-
 ```
@@
 #| warning: false
+# Load necessary libraries
 library(ggplot2)
 
+# Create ggplot
 analysis_data %>%
@@
 This upward trend is not confined to the past two decades only.
-South Asia has made a tremendous progress in female literacy rate which was only 21.27 percent in 1975[@The_World_Bank_2024b].
+South Asia has made a tremendous progress in female literacy rate which was only 21.27 percent in 1975[@The_World_Bank_Literacy].
 
@@
 Fertility rate in South Asia has long been on a decline.
-The South Asian fertility rate was as high as 6.07 births per woman in 1960[@The_World_Bank_2024c].
+The South Asian fertility rate was as high as 6.07 births per woman in 1960[@The_World_Bank_Fertility].
 

### 2024-04-19 paper/paper.qmd
update paper.qmd

@@
 
-The data was cleaned and analyzed using the 'R' programming language[@citeR] and the following packages were used: 'tidyverse' [@tidyverse], 'janitor' [@janitor],`dplyr` [@Dplyr], `ggplot2` [@citeggplot2], `here` [@herePackage], `kableExtra` [@citekableExtra], `knitr` [@knitr], `modelsummary` [@model], `readr` [@readr], `tibble` [@tibblePackage] and 'arrow' [@arrow]
+The data was cleaned and analyzed using the `R` programming language[@citeR] and the following packages were used: `tidyverse` [@tidyverse], `janitor` [@janitor],`dplyr` [@Dplyr], `ggplot2` [@citeggplot2], `here` [@herePackage], `kableExtra` [@citekableExtra], `knitr` [@knitr], `modelsummary` [@model], `readr` [@readr], `tibble` [@tibblePackage] and `arrow` [@arrow]
 
@@
 
-# Discussion
-
-## Growth in Female Literacy Rate in South Asia
-
-As analyzed in @fig-1,  the female literacy rate in South Asia is on the rise over the last two decades with a literacy rate of approximately 44.9 percent in the year 2000 to approximately 64.6 percent in 2020.
-This upward trend is not confined to the past two decades only.
-South Asia has made a tremendous progress in female literacy rate which was only 21.27 percent in 1975[@The_World_Bank_Literacy].
-
-## Declining Fertility Rate (total births per woman)in South Asia
-
-As analyzed in @fig-2,  the fertility rate in South Asia is on the decline over the last two decades with a fertility rate of approximately 3.57 births per woman in the year 2000 to approximately 2.26 births per woman in 2020.
-This downward trend is not confined to the past two decades only.
-Fertility rate in South Asia has long been on a decline.
-The South Asian fertility rate was as high as 6.07 births per woman in 1960[@The_World_Bank_Fertility].
-
-## Impact of Female Literacy Rate on Fertility Rate
-
 \newpage
